Calendar-based graphics for visualising people's daily schedules

### 2017-06-28 main.Rmd
start looking at china pm2.5 data
added opening paragraph

## Construction

@@

## Reference lines and grids

@@

## Extensions

@@

## Application

>>>>

Calendar-based visualisation proves useful in unfolding human-related activities in temporal context. For example, @van_wijk_cluster_1999 developed a calendar view of heatmap to represent the number of employees in the office over a year, where colours indicate different clusters derived from the days. It effectively contrasts weekdays and weekends, highlights public holiday, and presents other known seasons like school vacations, all of which have influence over the turn-outs in the office. However, their technique is too constrained to colour-encoding graphics, we shall extend this calendar-based arrangement to allow for a broader range of glyphs using linear algebra tools. It has been implemented into the `sugrrants` package using [@r].

This work is motivated by studying hourly foot traffic in Melbourne city. Visualisation provides insights into understanding people's daily schedules or patterns, but it is often a difficult task to visually represent such type of data at the overall level. For example, pedestrian counts in city centre collected at hourly intervals would help with understanding the pulse of city life or improvement of district administration management. However, (1) this kind of data is typically related to multiple seasonal types including time of day, day of week, day of year; (2) owing to higher than daily frequency, the data is usually coupled with long time span; (3) most variations arise from days of week due to normal human activities, and it is of most interest to inspect days as a basic time unit. [@van_wijk_cluster_1999] developed a calendar-based heatmap to visualise (some data), which clearly contrasted weekday versus weekend effects.  Information-dense visual encoding that provides maximal information at the overall level.

# Construction

(NEED A BRIEF INTRO HERE)

## Calendar grids

@@

## Scales

## Reference lines and labels

@@

# Extensions

@@

# Applications
